Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-11 vesicle_code/docs/permeableVes/main.tex
put capillary number in Fig 3 rather than shear rate
fixed capillary number notation
put in pdf for shear composite
yny

@@

In microfluidic experiments, it is challenging to keep a freely
suspended red blood cell or vesicle in a steady flow for more than a few
hours. It is also difficult to quantify the vesicle area/volume ratio
accurately.  Using numerical simulations we can quantify the effects of
water permeability on the hydrodynamics of a vesicle under mechanical
stresses. 
In the absence of an osmotic gradient, we first show that
a freely suspended semipermeable vesicle behaves differently from an
impermeable vesicle over a long time. Next we show that, at normal
physiological conditions, the permeable water flow can be amplified by
extreme confinement and results in observable change in both vesicle
hydrodynamics and reduced area. These results will shed light on the
dynamic aging process of living cells that constantly go through flows
and constrictions over a period of days.

@@

We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
$Ca_\mathrm{E}=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the system (see Supplementary Material) and
$\dot{\gamma}$ is the shear rate of the planar shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$.
 %with different permeability $\beta$ and shear rates $\dot{\gamma}$. 
 When $\beta=0$ (impermeable
case), a vesicle's reduced area and viscosity contrast determine whether
it tank treads or tumbles~\cite{fin-lam-sei-gom2008,
kra-win-sei-lip1996}. Focusing on semipermeable vesicles with no
viscosity contrast, we find that a semipermeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics, similar to the
case of an impermeable vesicle.

>>>>

\setboolean{displaywatermark}{false}

@@

In microfluidic experiments, it is challenging to keep a freely
suspended red blood cell or vesicle in a steady flow for more than a few
hours. It is also difficult to quantify the vesicle area/volume ratio
accurately \cite{MinetttiCallensCoupier2008_AppliedOptics}.  Using numerical simulations we can quantify the effects of
water permeability on the hydrodynamics of a vesicle under mechanical
stresses. 
In the absence of an osmotic gradient, we first show that
a freely suspended semipermeable vesicle behaves differently from an
impermeable vesicle over a long time. Next we show that, at normal
physiological conditions, the permeable water flow can be amplified by
extreme confinement and results in observable change in both vesicle
hydrodynamics and reduced area. These results will shed light on the
dynamic aging process of living cells that constantly go through flows
and constrictions over a period of days.

@@

We consider a semipermeable vesicle in a planar shear flow, characterized by the elastic capillary number
$Ca_\mathrm{E}=\dot{\gamma}\tau$, where $\tau$ is the characteristic time scale in the non-dimensionalization (see Supplementary Material) and
$\dot{\gamma}$ is the shear rate of the planar shear flow
$\uu_{\infty}(\xx) = \dot{\gamma} (y,0)$.
 %with different permeability $\beta$ and shear rates $\dot{\gamma}$. 
 When $\beta=0$ (impermeable
case), a vesicle's reduced area and viscosity contrast determine whether
it tank treads or tumbles~\cite{fin-lam-sei-gom2008,
kra-win-sei-lip1996}. Focusing on semipermeable vesicles with no
viscosity contrast, we find that a semipermeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics, similar to the
case of an impermeable vesicle.
